Lexicalized Domain Representations for Neural Machine Translation

### 2019-05-20 2019/emnlp/sparse.tex
discuss most results, fix a couple of problems with the bib

\subsection{Results}
Discussion 1:
\begin{itemize}
\item transformer better than RNN
\item Fine tuning is the best strategy - but subject to catastrophic
\item Sparse better than joint - better than domain control
\item Across th board / language \& architecture - always good for EMEA , less good for EPPS, varying for ECB
\item better ? than domain control ? WMCD ?
\end{itemize}

Discussion 2:
\begin{itemize}
\item Sparse 1 > Sparse 2
\item out of domain better than Mixed
\item Sparse 3 ??
\item ajouter Sparse 4
\end{itemize}

\begin{table*}[!h]
\begin{center}
\scalebox{1.0}{
\begin{tabular}{|l|ccc|ccc||c|}
\hline
Model & EMEA & EPPS & ECB & khreshmoi & newstest2014 & iwslt2010 & Avg. \\
\hline
\multicolumn{8}{l}{English$\rightarrow$French} \\
\hline
$Mixed$ & 67.69$_{47.60}$ & 37.50 & 53.49 & 34.86 & 28.56 & 25.70 & avg \\
\hline
$FT_{EMEA}$ & 76.77$_{49.43}$ & 17.16 & 11.99 & 29.58 & 11.64 & 11.10 & avg \\
$FT_{EPPS}$ & 20.86 & 37.04 & 24.53 & 31.86 & 28.33 & 11.10 & avg \\
$FT_{ECB}$   & 26.93 & 27.09 & 56.52 & 22.04 & 17.51 & 13.99 & avg \\
\hline
$DC$ & 67.87$_{45.42}$ & 37.31 & 54.14 & 33.63 & 26.52 & 24.81 & avg\\
\hline
$LDR_{oracle}$   & 74.26$_{49.90}$ & 37.67 & 54.07 & 33.85 & 28.11 & 25.70 & avg \\
$LDR^{v2}_{oracle}$   & 74.95$_{49.38}$ & 37.35 & 55.91 & 33.57 & 27.59 & 25.27 & avg \\
$LDR_{generic}$ & 73.97$_{49.54}$ & 37.81 & 53.67 & 34.17 & 28.11 & 25.70 & avg \\
$LDR_{rnn}$ & EMEA & EPPS & ECB & khreshmoi & newstest & iwslt & avg \\
$LDR_{wrong}$ & 72.95$_{49.78}$ & 37.62 & 53.35 & khreshmoi & newstest & iwslt & avg\\
\hline
\multicolumn{8}{l}{English $\rightarrow$German} \\
\hline
$Mixed$ & 64.57$_{42.99}$ & 26.47 & 68.67 & 21.77 & 17.04 & 18.85 & avg \\
\hline
$FT_{EMEA}$ & 68.35 & 17.02 & 32.87 & 21.15 & 11.21 & 13.49 & avg\\
$FT_{EPPS}$ & 36.19 & 26.29 & 40.71 & 19.67 & 16.47 & 19.24 & avg \\
$FT_{ECB}$   & 24.72 & 18.36 & 74.05 & 11.31  & 10.8 & 11.00 & avg \\
\hline
$DC$ & 63.48$_{42.98}$ & 26.27 & 66.95 & 21.45 & 16.45 & 18.78 & avg \\
\hline
$LDR_{oracle}$ & 70.9$_{46.12}$ & 26.30 & 68.9 & 21.42 & 16.57 & 18.82 & avg \\
$LDR^{v2}_{oracle}$ & 71.31$_{45.23}$ & 25.98 & 73.74 & 21.6 & 16.37 & 19.2 & avg \\
$LDR_{generic}$ & 70.86$_{45.60}$ & 26.14 & 68.59 & 21.95 & 16.57 & 18.82 & avg\\
$LDR_{rnn}$ & EMEA & EPPS & ECB & khreshmoi & newstest & iwslt & avg \\
$LDR_{wrong}$ & 69.51$_{43.50}$ & 26.31 & 66.86 & khreshmoi & newstest & iwslt & avg \\
\hline
\end{tabular}
} %scalebox
\end{center}
\caption{BPE-detokenized BLEU scores for the Transformer architecture over test sets.}
\end{table*}

\begin{table*}[!h]
\begin{center}
\scalebox{1.0}{
\begin{tabular}{|l|ccc|ccc||c|}
\hline
Model & EMEA & EPPS & ECB & khreshmoi & newstest2014 & iwslt2010 & Avg. \\
\hline
\multicolumn{8}{l}{English$\rightarrow$French} \\
\hline
$Mixed$               & 65.42$_{45.11}$ & 34.7 & 51.38 & 29.27 & 22.21 & 21.63 & avg \\
\hline
$FT_{EMEA}$     & 72.06 $ $ & 18.62 & 16.78 & 25.88 & 10.94 & 5.73 & avg \\
$FT_{EPPS}$      & 35.47 $ $ & 34.61 & 39.56 & 27.11 & 21.85 & 20.61 & avg \\
$FT_{ECB}$        & 21.93 $ $ & 22.6 & 51.53 & 14.74 & 12.10 & 10.47 & avg \\
\hline
$DC$                   & 68.26 $_{43.76}$ & 35.13 & 50.09 & 27.86 & 20.95 & 21.16 & avg \\
 \hline
$WDCMT$           & 68.76 $_{45.29}$ & 35.71 & 52.75 & 32.03 & 24.63 & 23.28 & avg \\
\hline
$LDR_{oracle}$   & 71.73 $_{46.30}$ & 35.21 & 50.91 & 29.62 & 23.00 & 20.96 & avg\\
$LDR_{generic}$ & 70.59 $_{46.37}$ & 35.22 & 49.68 & 29.51 & 23.00 & 20.96 & avg\\
$LDR_{rnn}$        & EMEA & EPPS & ECB & khreshmoi & newstest & iwslt & avg\\
$LDR_{wrong}$   & 62.1 $_{43.29}$ & 34.17 & 48.79 & khreshmoi & newstest & iwslt & avg \\
\hline
\multicolumn{8}{l}{English$\rightarrow$German} \\
\hline
$Mixed$               & 57.37 $_{37.94}$ & 23.1 & 63.54 & 17.39 & 11.51 & 14.29 & avg\\
\hline
$FT_{EMEA}$      & 65.64 $ $ & 12.36 & 15.93 & 15.38 & 6.22 & 7.6  & avg\\
$FT_{EPPS}$       & 24.90 $ $ & 22.98 & 26.26 & 13.55 & 11.33 & 14.32 & avg \\
$FT_{ECB}$         & 41.8 $ $ & 15.97 & 71.07 & 10.77 & 7.66 & 8.07 & avg\\
\hline
$DC$                    & 62.53 $_{39.25}$ & 23.74 & 65.71 & 16.88 & 11.15 & 14.97 & avg\\
\hline
WDCMT               & 64.05 $_{38.54}$ & 22.82 & 67.00 & 15.94 & 11.45 & 13.66 & avg\\
\hline
$LDR_{oracle}$   & 63.43 $_{40.04}$ & 22.66 & 64.40 & 16.99 & 11.45 & 14.26 & avg\\
$LDR_{generic}$ & 63.27 $_{39.75}$ & 22.62 & 63.70 & 17.26 & 11.45 & 14.26 & avg\\
$LDR_{rnn}$        & EMEA & EPPS & ECB & khreshmoi & newstest & iwslt & avg\\
$LDR_{wrong}$   & 56.84 $_{37.05}$ & 22.06 & 61.66 & khreshmoi & newstest & iwslt & avg \\
\hline
\end{tabular}
} %scalebox
\end{center}
\caption{BPE-detokenized BLEU scores for the RNN architecture over test sets.}
\end{table*}

\section{Discussion\label{sec:Discussion}}
\subsection{Sparse's performance}
First, we analyze the performance of models on inner test sets which are created by randomly splited from same corpora as training set. The 4 table show remarquable improvement 6 points BLEU in average in EMEA translation which is comparable with finetuned model. In all most the cases, Sparse model has slightly higher score on EPPS test and ECB test than mixed and finetuned models. Sparse model also achieve comparable scores with Domain Control and WDCMT in average. In considering the score of finetuned model on out-of-domain test sets, we observed a fast catastrophic forgetting while the out-of-domain scores drop dramatically compared to mixed model. Taking into account the average score on 3 inner test sets, Sparse achieved far better score than all finetuned models. \\
Secondly, we compare performance of models on IWSLT test 2010 and newstest 2014 which are more general than inner test sets. On these test sets, mixed, Sparse has approximately same score in Transformer and are a little better than Domain Control while in Recurrent Net Work architecture, WDCMT is better than mixed, Sparse and Domain Control for English -French pair. We also noted a quick fall of performance in finetuned model.

\subsection{Region's size \label{secc:region_size}}

We also test different setting of region size in word embedding. However, we limit our research in 4 settings: $[4,4,4,496]$, $[8,8,8,488]$, $[16,16,16,464]$, $[32,32,32,32,416]$. We test those settings with the same condition as above. The scores are in Table~\ref{tab:embedding-size}.\fyTodo{Comment, homegenize captions.}

Results are very close so we pick 8.\fyTodo{Experiment with 64}.

\begin{table*}[!h]
\begin{center}
\scalebox{1.0}{
\begin{tabular}{|l|ccc|ccc|}
\hline
$LDR$ & EMEA & EPPS & ECB & khreshmoi & newstest2014 & iwslt2010 \\
\hline
\multicolumn{7}{l}{English$\rightarrow$French} \\
\hline
 size=4   & 74.65 $_{49.61}$ & 37.42 & 54.49 & 33.68 & 28.03 & 25.28 \\
 size=8   & 74.26 $_{49.90}$ & 37.67 & 54.07 & 33.85 & 28.11 & 25.70 \\
 size=16 & 74.15 $_{49.10}$ & 37.78 & 54.56 & 33.40 & 28.10 & 25.33 \\
 size=32 & 75.10 $_{48.61}$ & 37.64 & 54.29 & 33.20 & 27.99 & 25.44 \\
 size=64 & 74.5 $_{50.17}$ & 37.27 & 54.5 & 33.26 & 27.95 & 25.65 \\
\hline
\end{tabular}
} %scalebox
\end{center}
\caption{BPE-detokenized BLEU scores for the RNN architecture over test sets.}
\end{table*}

@@

Multi-domain Machine Translation has largely interested NLP community by its promising applications in industry and its relation to fundamental problems in theory. Researchers have proposed a large range of techniques from Data centric methods to Model centric methods \cite{Chu18asurvey}.\\ Data centric category attempts to collect related-domain data from large existing in-domain corpora. The methods in this category can be listed as following:
\fyTodo{Organize refs}

\begin{itemize}
\item score relatedness of sentences to the target domain by Language Model \cite{Moore2010selection,Axelrod2011domain,Duh2013selection}.
\item generating pseudo parallel data \cite{Utiyama2003measure,Wang2016connecting,Wang2014neural}
\end{itemize}
On the other hand, model-centric approaches focus on NMT models that are specialized for domain adaptation. The novelty can be among following features:
\begin{itemize}
\item Trainining objective\cite{Luong2015SNMT,Sennrich2016Mono,Wang17instance,Chen17costweighting,Miceli2017Regularize,Zhang18sentence}
\item Architecture \cite{gulcehre2016monolingual,Zhang16topicinformed,Kobus17domaincontrol,Britz2017mixing,Biao2017CARENMT,Britz2017mixing,Thompson18freezing,Michel2018extreme}.
\item The decoding algorithm \cite{gulcehre2016monolingual,Khayrallah2017lattice}
\end{itemize}
Beside these works \fyTodo{Works= oeuvres d'art}, we could also consider works in other tasks such as sequence labeling tasks \cite{Daume07frustratingly}; learning multiple visual domains \cite{Rebuffi2017Visual}.

@@

The most common adaptation scenario is using (mostly) out-of-domain training data while testing on a low-resource domain.  In this setting, data-based approaches aim to bias the distribution of the train (out-of-domain) data towards matching that of the target domain, using data selection techniques  \cite{Moore2010selection,Axelrod2011domain,Duh2013selection}, or generating adapted pseudo-parallel data through back-translation  \cite{Utiyama2003measure,Wang2014neural,Wang2016connecting,Sennrich2016Mono}. Model-centric approaches build domain-adapted models by combining (eg.\ with mixture weights) multiple data sources or multiple systems \cite{Foster07mixture,Wang17instance}, or by biasing the training objective towards the desired domain using in-domain adaptation data \cite{Luong2015SNMT,Freitag2016FastDA,Chen17costweighting}. Another approach worth mentioning integrates domain information (for instance a domain language model) in the decoding algorithm \cite{Gulcehre2016monolingual}.

>>>>

\subsection{Results}
% Discussion 1:
% \begin{itemize}
% \item transformer better than RNN
% \item Fine tuning is the best strategy - but subject to catastrophic
% \item Sparse better than joint - better than domain control
% \item Across th board / language \& architecture - always good for EMEA , less good for EPPS, varying for ECB
% \item better ? than domain control ? WMCD ?
% \end{itemize}

% Discussion 2:
% \begin{itemize}
% \item Sparse 1 > Sparse 2
% \item out of domain better than Mixed
% \item Sparse 3 ??
% \item ajouter Sparse 4
% \end{itemize}

Our main results are summarized respectively in Table~\ref{tab:results-trsf} for the Transformer systems and Table~\ref{tab:results-rnn} for the RNN systems. \fyTodo{Check missing numbers in Table}.

We first concentrate on the left part of these tables, where we analyze the performance for the three domains of interest. A first series of observations is that Transformer is consistently better than RNN, and that fine-tuning on a domain-specific corpus, when applicable, is the best way to optimize the performance on that domain, albeit at the cost of a marked (even sometimes catastrophic, eg.\ for the EMEA-tuned Transformer system) decrease in performance for the other domains.

For these test sets, our proposal (\texttt{LDR}$_{oracle}$) is consistently better that the mix-domain strategy, with gains than range from very large (for EMEA and ECB) to unsignificant (for EPPS in most conditions). This means that our architecture is somehow able to compensate for the data unbalance, and to raise the performance of the multi-domain system close to the best (fine-tuned) system in each domain. We even observe rare cases where the \texttt{LDR}$_{oracle}$ system outperforms fine-tuning (eg.\ Transformer en:ge). \texttt{LDR}$_{oracle}$ is also better than Domain Control in three conditions out of four, \texttt{DC} being seemingly a better choice for the RNN than for the Transformer architecture. The comparison with the WCDMT model is less favourable for our RNN systems, which are arguably much simpler.\fyTodo{More on this.}
As expected, ignoring the domain label yields a drop in performance for the two fallback strategies considered in this study. The first, \texttt{LDR}$_{generic}$, only use the generic embeddings. The second, \texttt{LDR}$_{pred}$\fyTodo{Fix this}, resorts to automatically predicted domain labels.\fyTodo{Explain how} Note that this decrease is however quite limited\fyTodo{How much on average ?}, showing that our architecture is quite robust to noisy labels. Even in the worst case scenario where all domain tags are intently wrong (\texttt{LDR}$_{wrong}$), we see that the generic part still ensures a satisfying level of performance.\fyTodo{Comment V2 from Minh}

The right part of Tables~\ref{tab:results-trsf} and \ref{tab:results-rnn} report performance on test sets for new domains not seen in training. Khresmoi texts, which are extracted from summaries of medical article are assumed to from the same domain as EMEA data; for the other two test sets, we assume no domain and only use the generic embeddings. Here, we see that our best system \texttt{LDR}$_{oracle}$ is slightly lagging behind the \texttt{Mixed} baselines (the difference ranges from unsignificant to one Bleu point), which can be attributed to larger useful (generic) embedding in the \texttt{Mixed} setting. Here again, we see that using the sole generic part makes the system robust with respect to unknown or misleading domain tags. We finally outline that our approach outperforms DC for these test sets (were we have to predict a tag)\fyTodo{Fix this}, and even outperforms WCDMT, which has no built in mechanism to handle data from unknown domains.

\begin{table*}[!h]
\begin{center}
\scalebox{1.0}{
\begin{tabular}{|l|ccc|ccc||c|}
\hline
Model & EMEA & EPPS & ECB & Khresmoi & NewsTest2014 & IWSLT2010 & Avg. \\
\hline
\multicolumn{8}{l}{} \\[-9pt]  
\multicolumn{8}{l}{English$\rightarrow$French} \\
\hline
$Mixed$ & 67.69$_{47.60}$ & 37.50 & 53.49 & 34.86 & 28.56 & 25.70 & avg \\
\hline
$FT_{EMEA}$ & 76.77$_{49.43}$ & 17.16 & 11.99 & 29.58 & 11.64 & 11.10 & avg \\
$FT_{EPPS}$ & 20.86 & 37.04 & 24.53 & 31.86 & 28.33 & 11.10 & avg \\
$FT_{ECB}$   & 26.93 & 27.09 & 56.52 & 22.04 & 17.51 & 13.99 & avg \\
\hline
$DC$ & 67.87$_{45.42}$ & 37.31 & 54.14 & 33.63 & 26.52 & 24.81 & avg\\
\hline
$LDR_{oracle}$   & 74.26$_{49.90}$ & 37.67 & 54.07 & 33.85 & 28.11 & 25.70 & avg \\
$LDR^{v2}_{oracle}$   & 74.95$_{49.38}$ & 37.35 & 55.91 & 33.57 & 27.59 & 25.27 & avg \\
$LDR_{generic}$ & 73.97$_{49.54}$ & 37.81 & 53.67 & 34.17 & 28.11 & 25.70 & avg \\
$LDR_{rnn}$ & EMEA & EPPS & ECB & khreshmoi & newstest & iwslt & avg \\
$LDR_{wrong}$ & 72.95$_{49.78}$ & 37.62 & 53.35 & khreshmoi & newstest & iwslt & avg\\
  \hline
\multicolumn{8}{l}{} \\[-9pt]
\multicolumn{8}{l}{English $\rightarrow$German} \\
\hline
$Mixed$ & 64.57$_{42.99}$ & 26.47 & 68.67 & 21.77 & 17.04 & 18.85 & avg \\
\hline
$FT_{EMEA}$ & 68.35 & 17.02 & 32.87 & 21.15 & 11.21 & 13.49 & avg\\
$FT_{EPPS}$ & 36.19 & 26.29 & 40.71 & 19.67 & 16.47 & 19.24 & avg \\
$FT_{ECB}$   & 24.72 & 18.36 & 74.05 & 11.31  & 10.8 & 11.00 & avg \\
\hline
$DC$ & 63.48$_{42.98}$ & 26.27 & 66.95 & 21.45 & 16.45 & 18.78 & avg \\
\hline
$LDR_{oracle}$ & 70.9$_{46.12}$ & 26.30 & 68.9 & 21.42 & 16.57 & 18.82 & avg \\
$LDR^{v2}_{oracle}$ & 71.31$_{45.23}$ & 25.98 & 73.74 & 21.6 & 16.37 & 19.2 & avg \\
$LDR_{generic}$ & 70.86$_{45.60}$ & 26.14 & 68.59 & 21.95 & 16.57 & 18.82 & avg\\
$LDR_{rnn}$ & EMEA & EPPS & ECB & khreshmoi & newstest & iwslt & avg \\
$LDR_{wrong}$ & 69.51$_{43.50}$ & 26.31 & 66.86 & khreshmoi & newstest & iwslt & avg \\
\hline
\end{tabular}
} %scalebox
\end{center}
\caption{BPE-detokenized BLEU scores for the Transformer architecture \label{tab:results-trsf}}
\end{table*}

\begin{table*}[!h]
\begin{center}
\scalebox{1.0}{
\begin{tabular}{|l|ccc|ccc||c|}
\hline
Model & EMEA & EPPS & ECB & Khresmoi & NewsTest2014 & IWSLT2010 & Avg. \\
\hline
\multicolumn{8}{l}{} \\[-9pt]
\multicolumn{8}{l}{English$\rightarrow$French} \\
\hline
$Mixed$               & 65.42$_{45.11}$ & 34.7 & 51.38 & 29.27 & 22.21 & 21.63 & avg \\
\hline
$FT_{EMEA}$     & 72.06 $ $ & 18.62 & 16.78 & 25.88 & 10.94 & 5.73 & avg \\
$FT_{EPPS}$      & 35.47 $ $ & 34.61 & 39.56 & 27.11 & 21.85 & 20.61 & avg \\
$FT_{ECB}$        & 21.93 $ $ & 22.6 & 51.53 & 14.74 & 12.10 & 10.47 & avg \\
\hline
$DC$                   & 68.26 $_{43.76}$ & 35.13 & 50.09 & 27.86 & 20.95 & 21.16 & avg \\
 \hline
$WDCMT$           & 68.76 $_{45.29}$ & 35.71 & 52.75 & 32.03 & 24.63 & 23.28 & avg \\
\hline
$LDR_{oracle}$   & 71.73 $_{46.30}$ & 35.21 & 50.91 & 29.62 & 23.00 & 20.96 & avg\\
$LDR_{generic}$ & 70.59 $_{46.37}$ & 35.22 & 49.68 & 29.51 & 23.00 & 20.96 & avg\\
$LDR_{rnn}$        & EMEA & EPPS & ECB & khreshmoi & newstest & iwslt & avg\\
$LDR_{wrong}$   & 62.1 $_{43.29}$ & 34.17 & 48.79 & khreshmoi & newstest & iwslt & avg \\
\hline
\multicolumn{8}{l}{} \\[-9pt]
\multicolumn{8}{l}{English$\rightarrow$German} \\
\hline
$Mixed$               & 57.37 $_{37.94}$ & 23.1 & 63.54 & 17.39 & 11.51 & 14.29 & avg\\
\hline
$FT_{EMEA}$      & 65.64 $ $ & 12.36 & 15.93 & 15.38 & 6.22 & 7.6  & avg\\
$FT_{EPPS}$       & 24.90 $ $ & 22.98 & 26.26 & 13.55 & 11.33 & 14.32 & avg \\
$FT_{ECB}$         & 41.8 $ $ & 15.97 & 71.07 & 10.77 & 7.66 & 8.07 & avg\\
\hline
$DC$                    & 62.53 $_{39.25}$ & 23.74 & 65.71 & 16.88 & 11.15 & 14.97 & avg\\
\hline
WDCMT               & 64.05 $_{38.54}$ & 22.82 & 67.00 & 15.94 & 11.45 & 13.66 & avg\\
\hline
$LDR_{oracle}$   & 63.43 $_{40.04}$ & 22.66 & 64.40 & 16.99 & 11.45 & 14.26 & avg\\
$LDR_{generic}$ & 63.27 $_{39.75}$ & 22.62 & 63.70 & 17.26 & 11.45 & 14.26 & avg\\
$LDR_{rnn}$        & EMEA & EPPS & ECB & khreshmoi & newstest & iwslt & avg\\
$LDR_{wrong}$   & 56.84 $_{37.05}$ & 22.06 & 61.66 & khreshmoi & newstest & iwslt & avg \\
\hline
\end{tabular}
} %scalebox
\end{center}
\caption{BPE-detokenized BLEU scores for the RNN architecture \label{tab:results-rnn}}
\end{table*}
% \clearfloat

\section{Discussion\label{sec:Discussion}}
% \subsection{Sparse's performance}
% First, we analyze the performance of models on inner test sets which are created by randomly splited from same corpora as training set. The 4 table show remarquable improvement 6 points BLEU in average in EMEA translation which is comparable with finetuned model. In all most the cases, Sparse model has slightly higher score on EPPS test and ECB test than mixed and finetuned models. Sparse model also achieve comparable scores with Domain Control and WDCMT in average. In considering the score of finetuned model on out-of-domain test sets, we observed a fast catastrophic forgetting while the out-of-domain scores drop dramatically compared to mixed model. Taking into account the average score on 3 inner test sets, Sparse achieved far better score than all finetuned models. \\
% Secondly, we compare performance of models on IWSLT test 2010 and newstest 2014 which are more general than inner test sets. On these test sets, mixed, Sparse has approximately same score in Transformer and are a little better than Domain Control while in Recurrent Net Work architecture, WDCMT is better than mixed, Sparse and Domain Control for English -French pair. We also noted a quick fall of performance in finetuned model.

\subsection{Balancing generic and domain-specific representations\label{secc:region_size}}

An important practical question concerns the balance between the generic and the domain-specific part of the embedding. In the limit where the domain specific part is very small, we should recover the performance of the \texttt{Mixed} system; conversely, we expect to see a less effective sharing of data across domains by increasing the domain-specific regions. Table~\ref{tab:embedding-size} reports the result of  a series of experiments for the Transformer\fyTodo{Check This} architecture with varying domain-specific sizes allocating between 4 and 64 cells for domain-specific information, and the complement to 512 for the generic part. The differences being overall quite small \fyTodo{Comments - is this due to prior ?}, we decided to allocate $8$ cells for the domain specific part. \fyTodo{Easily accomodate more domains}
\fyTodo{Given the ways embeddings are computed, why not add more domains, and test robustness agains data presentation order ?}
\begin{table*}[!h]
\begin{center}
\scalebox{1.0}{
\begin{tabular}{|l|ccc|ccc|}
\hline
$LDR$ & EMEA & EPPS & ECB & khreshmoi & newstest2014 & iwslt2010 \\
\hline
\multicolumn{7}{l}{English$\rightarrow$French} \\
\hline
 size=4   & 74.65 $_{49.61}$ & 37.42 & 54.49 & 33.68 & 28.03 & 25.28 \\
 size=8   & 74.26 $_{49.90}$ & 37.67 & 54.07 & 33.85 & 28.11 & 25.70 \\
 size=16 & 74.15 $_{49.10}$ & 37.78 & 54.56 & 33.40 & 28.10 & 25.33 \\
 size=32 & 75.10 $_{48.61}$ & 37.64 & 54.29 & 33.20 & 27.99 & 25.44 \\
 size=64 & 74.5 $_{50.17}$ & 37.27 & 54.5 & 33.26 & 27.95 & 25.65 \\
\hline
\end{tabular}
} %scalebox
\end{center}
\caption{BPE-detokenized BLEU scores for the Transformer architecture for varying domain-specific embedding sizes}
\end{table*}

@@

% Multi-domain Machine Translation has largely interested NLP community by its promising applications in industry and its relation to fundamental problems in theory. Researchers have proposed a large range of techniques from Data centric methods to Model centric methods \cite{Chu18asurvey}.\\ Data centric category attempts to collect related-domain data from large existing in-domain corpora. The methods in this category can be listed as following:
% \fyTodo{Organize refs}

% \begin{itemize}
% \item score relatedness of sentences to the target domain by Language Model \cite{Moore2010selection,Axelrod2011domain,Duh2013selection}.
% \item generating pseudo parallel data \cite{Utiyama2003measure,Wang2016connecting,Wang2014neural}
% \end{itemize}
% On the other hand, model-centric approaches focus on NMT models that are specialized for domain adaptation. The novelty can be among following features:
% \begin{itemize}
% \item Trainining objective\cite{Luong2015SNMT,Sennrich2016Mono,Wang17instance,Chen17costweighting,Miceli2017Regularize,Zhang18sentence}
% \item Architecture \cite{Gulcehre2016monolingual,Zhang16topicinformed,Kobus17domaincontrol,Britz2017mixing,Biao2017CARENMT,Britz2017mixing,Thompson18freezing,Michel2018extreme}.
% \item The decoding algorithm \cite{Gulcehre2016monolingual,Khayrallah2017lattice}
% \end{itemize}
% Beside these works \fyTodo{Works= oeuvres d'art}, we could also consider works in other tasks such as sequence labeling tasks \cite{Daume07frustratingly}; learning multiple visual domains \cite{Rebuffi2017Visual}.

@@

The most common adaptation scenario uses (mostly) out-of-domain data in training, while testing on a low-resource in-domain set of texts. In this setting, \emph{data-based approaches} aim to bias the distribution of the train (out-of-domain) data towards matching that of the target domain, using data selection techniques \cite{Moore2010selection,Axelrod2011domain,Duh2013selection}, or generating adapted pseudo-parallel data through back-translation  \cite{Utiyama2003measure,Wang2014neural,Wang2016connecting,Sennrich2016Mono}. \emph{Model-centric approaches} build domain-adapted models by combining (eg.\ with mixture weights) multiple data sources or multiple systems \cite{Foster07mixture,Wang17instance}, or by biasing the training objective towards the desired domain using in-domain adaptation data \cite{Luong2015SNMT,Freitag2016FastDA,Chen17costweighting}. Another approach worth mentioning integrates domain information (for instance a domain language model) in the decoding algorithm \cite{Gulcehre2016monolingual}.
